The Astropy Project:

### 2017-09-21 main.tex
whitespace
Update on Overleaf.

\begin{itemize}
	\item We don't plan on including code in this paper, but if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository. 
    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename} not ``Figure''
\end{itemize}

@@

\subsection{Use of Quantities across package}

@@

% \subsection{Analytic Functions}

@@

\subsection{Coordinates}
% Adrian, Erik

@@

\textbf{Key features:}
\begin{itemize}
	\item Celestial coordinates, and local coordinates (via EarthLocation + Time)
	\item JPL ephemerids
\end{itemize}

\subsection{Units and quantities}
% Marten, Adrian

@@

\subsubsection{NDDdata}
% Matt C., Michael, or Steve C.

\subsubsection{Tables}
% Tom A.
QTable is new, mixin columns for time and coordinates. Table operations were added in v0.3

@@

\subsection{Modeling}
% Nadia

The whole modeling submodule was missing from the previous paper, so everything really, including compound models, unit support etc.

\subsection{Visualization}
% Larry, Tom R.

@@

\subsection{Statistics}
% Steve C., Jake V.

major additions to be discussed: lomb-scargle, sigma clipping, bayesian blocks, histograms

\section{Infrastructure for affiliated packages}
\subsubsection{Package template}
bsipocz may write this up if there is no other takers
\subsection{Continuous integration helpers}
bsipocz should write this up
\subsection{sphinx extensions}
probably Tom R should write this up
\section{State of the Ecosystem}

@@

Who to thank?

>>>>

\begin{itemize}
   \item The goal is to produce a brief and informative paper that covers major astropy principles not mentioned in the first paper, the core v2.0 package, and infrastructure in astropy project to support development in python.   
	\item We don't plan on including code in this paper, but if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository.
    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename} not ``Figure''
    \item If your subpackage was included in Paper I, then please just include a note on what the package does, a reference to paper I, and any new major updates to your package
    \item If your subpackage was not included, then please a further description of the sub-package on level with what was in the first paper, and highlight any major features in it.   Typically length should be equivalent to one column

\end{itemize}

@@

\subsection{Use of Quantities across package}
% Marten and Tom R.

{\bf Very rough first text!}

Historically, it has been unusual to keep units as part of numbers, especially as speed was often deemed essential and quantities used to be slower than regular arrays. Hence, programs and functions expected to be fed parameters in particular units, as (hopefully) stated in their documentation.  In astropy 0.4, therefore, unit and quantity support was still somewhat spotty, but this has changed greatly.  One of the riskiest classes was ngles, where both degrees and radians were ``obvious'' default units to some. As a consequence, quantities are most fully integrated in the coordinates module (Sect.~\ref{sec:coordinates}). In astropy 2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see Sect.~\ref{sec:table}). As a result, units in fits tables are also well-supported. For most other modules, quantities are at least accepted, and often assumed by default.

In the process, some standard wrappers have been defined that make defining functions that require quantities as input simpler. As an extension of this, we plan to define wrappers for functions that work on numbers that will automatically convert quantities to any required units.

\subsection{Long term support of v2.0}
% This could also include information about the development cycle

@@

% \subsection{Analytic Functions}
% moved to models and depreciated -- 
% just here for completeness at the moment

\subsection{Units and quantities}
\label{sec:units}
% Marten, Adrian

@@

\subsection{Coordinates}
\label{sec:coordinates}
% Adrian, Erik

@@

\textbf{Key features:}
\begin{itemize}
	\item Celestial coordinates, and local coordinates (via EarthLocation + Time)
	\item JPL ephemerids
    \item Proper motions, radial velocities
\end{itemize}

Separately, talk about representations as vectors? (MHvK)

\subsection{Time}
\label{sec:time}

Q: does it make sense to refer forward to fits support, even though it is 3.0?

@@

\subsubsection{NDDdata}
% Matt C., Michael, or Steve C.
% Larry (nddata.utils)
NOTE (Larry), The package is nddata, which includes the NDData object.  Don't forget the nddata.utils functionality (e.g. Cutout2D, block\_reduce, etc.).

\subsubsection{Tables}
\label{sec:table}
% Tom A.
QTable is new, mixin columns for time and coordinates. Table operations were added in v0.3

\subsection{io}
% Simon

\subsection{Modeling}
\label{sec:modeling}
% Nadia
% Lim blackbody
% Tom R. -- unit support
The whole modeling submodule was missing from the previous paper, so everything really, including compound models, unit support etc.

@@

\subsection{Visualization}
% Larry:  Image visualization (stretching, scaling), RGB
% Tom R.:  WCSAxes

@@

%\subsection{Utils}
% Lim

\subsection{Cosmology}

\subsection{Statistics}
% Steve C.
% Jake V.:  Lomb-scargle, Bayesian blocks
% Larry:  sigma clipping, biweight stats
major additions to be discussed: lomb-scargle, sigma clipping, bayesian blocks, histograms, also:  robust (biweight) statistics

\section{Infrastructure for affiliated packages}
\subsubsection{Package template}
bsipocz may write this up if there is no other takers
\subsection{Continuous integration helpers}
bsipocz should write this up
\subsection{sphinx extensions}
probably Tom R should write this up

% \section{State of the Ecosystem}
% Commenting out unless a clear statement is added

@@

Who to thank?  numfocus,
